Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-16 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Reviewing English grammar from Introduction. Couple of commas, basically, and minor change for the sake of clarity when reading

Some time ago, our group faced the problem of diminishing funds for
buying new hardware. This was aggravated by the increasing maintenance costs and
extended downtime resulting from the continuous failures of existing
clusters.
Considering this, we leveraged our experience in the design of web
applications, including JavaScript, since their inception and other
volunteer and
unconventional distributed evolutionary computing systems to 
design and release a new free framework that would allow anyone to
create a volunteer distributed evolutionary computation (EC) experiment using cloud resources as
servers and browsers as clients.
% (Paloma) I think you should rewrite this whole sentence.
% For starters, focus in that you "leveraged" the problem through your deeply knowledge of... this and that. And "Thus/Then/Therefore", you decided... 
% (Mario) We leverage our experience in blah blah to design
% (Paloma) It may be... guess I was thinking in the noun, not in the
% transitive verb
% Please check if there's a problem here too.

@@

When developing volunteer based frameworks, designers must
also consider the whole {\em social} aspect in the design, with
issues related to security, trust and privacy among others. 
The computing system becomes a {\em techno-social system} \cite{vespignani2009predicting}.  
% (Paloma) Is the social aspect related to the word "safety"? It's not completely clear.
%a {\em social} aspect to the design of a
%computing system that makes it a {\em techno-social system}
In this paper, our intention is to
present the {\sf NodIO} framework and analyze it from two different
angles: the purely technical angle, including the decisions that went
into its features, and the social angle, to account on how the persons
that voluntarily choose to enter the web page running the experiment
determine its performance and how it can be modeled and, eventually,
predicted.

>>>>

Some time ago, our group faced the problem of diminishing funds for
buying new hardware. This was aggravated by the increasing maintenance costs and
extended downtime resulting from the continuous failures of existing
clusters.
Considering this, we leveraged our experience in the design of web
applications since their inception, including JavaScript, and other
volunteer and
unconventional distributed evolutionary computing systems to 
design and release a new free framework that would allow anyone to
create a volunteer distributed evolutionary computation (EC) experiment using cloud resources as
servers, and browsers as clients.
% (Paloma) I think you should rewrite this whole sentence.
% For starters, focus in that you "leveraged" the problem through your deeply knowledge of... this and that. And "Thus/Then/Therefore", you decided... 
% (Mario) We leverage our experience in blah blah to design
% (Paloma) It may be... guess I was thinking in the noun, not in the
% transitive verb
% Please check if there's a problem here too.

@@

When developing volunteer based frameworks, designers must
also consider the whole {\em social} aspect in the design, with
issues related to security, trust, and privacy among others. 
The computing system becomes then a {\em techno-social system} \cite{vespignani2009predicting}.  
% (Paloma) Is the social aspect related to the word "safety"? It's not completely clear.
%a {\em social} aspect to the design of a
%computing system that makes it a {\em techno-social system}
In this paper, our intention is to
present the {\sf NodIO} framework and analyze it from two different
angles: the purely technical angle, including the decisions that went
into its features, and the social angle, to account on how the persons
that voluntarily choose to enter the web page running the experiment
determine its performance and how it can be modeled and, eventually,
predicted.
